Deep Learning for Automatic Speech Recognition

### 2015-04-30 Paper/Paper.tex
Further refinements

\paragraph{} We will begin by giving a brief overview of the traditional approach toward ASR using Gaussian mixture models (GMMs). In the subsequent sections, we will look in depth at the DNN approach of \cite{DBLP:journals/taslp/DahlYDA12} and the CNN approach of \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}. We will look at the overall architecture of the two models, how unsupervised pre-training is used to improve performance, and how supervised training is used to tune both systems. We will then look at experimental results of both models compared to GMMs, and follow up with thoughts on the future of ASR.

@@

where $\inAngle{ \cdot }_\text{1}$ is a single step Gibbs sampled expectation. These terms are expectations in which nodes $i$ and $j$ cooccur given the training data and model. Given this insight, regular stochastic gradient descent can be performed and the parameters of a RBM fitted to training data.

\paragraph{} Now that we have an understanding of RBMs, we can shift our focus to DBNs. A \DBN is a multilayer model with undirected connections between the top two layers and directed between other layers. To train these models, \cite{DBLP:journals/neco/HintonOT06} had the insight to treat adjacent layers of nodes as RBMs. One starts with the bottom two layers and trains them as though they were a single RBM. Once those two layers are trained, then the top layer of the RBM is treated as the input layer of a new RBM with the layer above that layer acting as the hidden layer of the new RBM. The sliding window over the layers continues until the full DBN is trained.  After this, \cite{DBLP:journals/neco/HintonOT06} describe an "up-down" algorithm to further refine the learned weights. The learned parameters of this greedy approach can then be used as the parameters of a DNN as explained earlier.

@@

\paragraph{} \cite{DBLP:journals/taslp/DahlYDA12} report that their system relies on nationwide language model consisting of 1.5 million trigrams. For their acoustic model, then use a five hidden layer DNN with each layer containing 2,048 hidden units. Training the system from scratch on 24 hours of training data takes four days on a Dell T3500 workstation with an NVIDIA Tesla GPU. \cite{DBLP:journals/taslp/DahlYDA12} emphasize the importance of the GPU in obtaining acceptable training time, and that without it, training time would be 30x slower.

@@

\paragraph{} Both \cite{DBLP:journals/taslp/DahlYDA12} and \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} have shown that neural network architectures exhibit better performance over Gaussian Mixture Models. \cite{DBLP:journals/taslp/DahlYDA12} believes that a more capable first layer model provided by mean-covariance restricted Boltzmann machines will increase performance, while \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} plans to investigate unexpected improvements in large-scale speech recognition where they were absent in phone recognition tasks when using convolutional restricted Boltzmann machines. Both routes seem promising and are likely to produce improved error rates.

>>>>

\paragraph{} We will begin by giving a brief overview of the traditional approach toward ASR using Gaussian Mixture Models (GMMs). In the subsequent sections, we will look in depth at the DNN approach of \cite{DBLP:journals/taslp/DahlYDA12} and the CNN approach of \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}. We will look at the overall architecture of the two models, how unsupervised pre-training is used to improve performance, and how supervised training is used to tune both systems. We will then look at experimental results of both models compared to GMMs, and follow up with thoughts on the future of ASR.

@@

where $\inAngle{ \cdot }_\text{1}$ is a single step Gibbs sampled expectation. These terms are expectations in which nodes $i$ and $j$ active simultaneously given the training data and model. Given this insight, regular stochastic gradient descent can be performed and the parameters of a RBM fitted to training data.

\paragraph{} Now that we have an understanding of RBMs, we can shift our focus to DBNs. A \DBN is a multilayer model with undirected connections between the top two layers and directed between other layers. To train these models, \cite{DBLP:journals/neco/HintonOT06} had the insight to treat adjacent layers of nodes as RBMs. One starts with the bottom two layers and trains them as though they were a single RBM. Once those two layers are trained, then the top layer of the RBM is treated as the input layer of a new RBM with the layer above that layer acting as the hidden layer of the new RBM. The sliding window over the layers continues until the full DBN is trained.  After this, \cite{DBLP:journals/neco/HintonOT06} describe an "up-down" algorithm to further refine the learned weights. The learned parameters of this greedy approach can then be used as the parameters of a DNN as explained earlier in the discussion of Eqn. (\ref{eqn:dahlEq7}).

@@

\paragraph{} \cite{DBLP:journals/taslp/DahlYDA12} report that their system relies on nationwide language model consisting of 1.5 million trigrams. For their acoustic model, they use a five hidden layer DNN with each layer containing 2,048 hidden units. Training the system from scratch on 24 hours of training data takes four days on a Dell T3500 workstation with an NVIDIA Tesla GPU. \cite{DBLP:journals/taslp/DahlYDA12} emphasize the importance of the GPU in obtaining acceptable training time, and that without it, training time would be 30x slower.

@@

\paragraph{} Both \cite{DBLP:journals/taslp/DahlYDA12} and \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} have shown that neural network architectures exhibit better performance over Gaussian Mixture Models. \cite{DBLP:journals/taslp/DahlYDA12} believes that a more capable first layer model provided by mean-covariance restricted Boltzmann machines will increase performance, while \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} plans to investigate unexpected improvements in large-vocabulary speech recognition where they were absent in phone recognition tasks when using convolutional restricted Boltzmann machines. Both routes seem promising and are likely to produce improved error rates.
